Taken from V1.0 - Protocols: CRISPR/Cas9 (with HD) zebrafish zygote microinjection protocol

## 13Nov2019 CRISPR/Cas9 (with HD) zebrafish zygote microinjection protocol:

<!-- \hypertarget{protocol1}{protocol number 1} -->

**ssODN dilution:**

Stock ssODN (M743T HD) is concentrated to 5932 ng/µg, dilution is required for injection mix preperation.

Mix material by \textcolor{red}{Table 1}'s instructions on \textcolor{red}{ice}. Afterwards carry out vortex and spindown.

**Table 1 - ssODN dilution:**

```{r, echo=FALSE}

library(knitr)
library(kableExtra)
Material<-"dr_GNE_HDR"
Initial.Conc<-"5932 ng/µL"
DDW.Volume<- "11 µL"
Volume.To.Pick<-"1 µL"
Final.Concentration<-"12 µL"

DF<-data.frame(Material, Initial.Conc, DDW.Volume, Volume.To.Pick, Final.Concentration)
kable(DF, "latex", booktabs = TRUE)
```


**Cas9 protein dilution:**
Stock Cas9 (protein) is concentrated to 5000 ng/µg, dilution is required for injection mix preperation.

Mix material by \textcolor{red}{Table 2}'s instructions on \textcolor{red}{ice}. Afterwards carry out vortex and spindown.

**Table 2:**

| Material | Initial Concentration | Volume to pick | DDW  | final concontration | Final Volume |
|----------+-----------------------+----------------+------+---------------------+--------------|
| Cas9     | 5000 ng/µL            | 1 µL           | 4 µL | 1000 ng/µg          | 12 µL        |

**Cas9/gRNA complex formation**

Mix:

* DDW from \textcolor{red}{Table 3} microinjection mix.
* Cas9 from \textcolor{red}{Table 3} microinjection mix.
* gRNA from \textcolor{red}{Table 3} microinjection mix.

Place in incubation at 37°C for ~10 miutes.

**Injection mix:**

On \textcolor{red}{ice}, mix the following materials. Perform vortex and spindown.

**Table 3:**
```{r, table 3, echo = FALSE}
Material <- c("Cas9", "gRNA",
             "ssODN", "KCl",
             "DDW", "final volume")
Vol.To.Pick<- c(1,1,1,0.5,1.5,5)
Initial.Conc<- c(1000, 1020.75, 494.999, 3000, "-", "-")
Final.Concentration<-c(200,204.15,98.866,300,"-","-")

df<-data.frame(Material,Vol.To.Pick,Initial.Conc,Final.Concentration)

library(knitr)
library(kableExtra)
kable(df, "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```

**Scr7 Dilution:**

In a 50 ml falcon tube:

**Table 4:**

```{r, echo=FALSE}

library(knitr)
library(kableExtra)
Material<-"Scr7"
Initial.Conc<-"4 mM"
DDW.Volume<- "300 µL"
Volume.To.Pick<-"30 mL"
Final.Concentration<-"20 µM"

DF<-data.frame(Material, Initial.Conc, DDW.Volume, Volume.To.Pick, Final.Concentration)
kable(DF, "latex", booktabs = TRUE)
```

**DMSO Dilution:**

In a 50 ml falcon tube:

**Table 5:**

```{r, echo=FALSE}

library(knitr)
library(kableExtra)
Material<-"DMSO"
Initial.Conc<-"X mM"
DDW.Volume<- "300 µL"
Volume.To.Pick<-"30 mL"
Final.Concentration<-"20 µM"

DF<-data.frame(Material, Initial.Conc, DDW.Volume, Volume.To.Pick, Final.Concentration)
kable(DF, "latex", booktabs = TRUE)
```

**Injection:**

* After zf mate - TL type, injection volume ~2 nL of injection mix (table 3), inject embryos at 1-cell stage on agarose gel track plate (pre heated to 28.5°C).
* Keep a few embryos uninjected for negative control.
* After injection move to Scr7 medium.


