## Microinjections on November 13^th^:

*Date: November 13^th^, 2019*
Following protocol <!-- \hyperlink{protocol1}{{\color{purple}{\underline{number 1}}}}. -->

We got our \textcolor{blue}{first batch} which I now call \hypertarget{Batch number 1}{"Batch number 1"}.

### Batch table:

```{r, echo = FALSE}
library(tibble)
library(kableExtra)
batch.file<-tribble(
  ~Batch, ~Parents, ~`Date`, ~`Number of offsprings`, ~`Number of living offsprings`,
  "Batch 1", "TL find out which cell" ,"Nov 13 2019", 40 , 18
)
kable(batch.file, "latex", booktabs = TRUE)
```

Batch 1 compiles of 40 zygotes, 27 of which were microinjected by Hagai, 13 of which were injected by me.
See [\textcolor{purple}{my plate}](images/batch1TL_M743T_MI_Tom_nov_13_2019.jpg), or [\textcolor{purple}{Hagai's plate}](images/batch1TL_M743T_MI_hagai_nov_13_2019.jpg)

Due to distance between our lab and lab 3 where the microinjections took place, along with unawareness of lack of devices such as 10 µL pipettes, we performed the injections on 8-16 cell stage zygotes (Hagai and I).

In my case some of the microinjections did not enter the cell, most were inside the egg close to the cell.





\pagebreak{}{}

## Microinjection expertise examination Tom V Hagai

\definecolor{brownyellow}{cmyk}{0, 0.72, 0.88, 0.69}
*Date: December 10^th^, 2019*
After conducting Microinjections on November 13^th^, I have data about \textcolor{brownyellow}{larvae's survivability after injection}. Part of the experiment's objectives was to examine my skills vs Hagai's skills. 

[\textcolor{purple}{Raw data - my table}](tables/Tom_VS_Hagai_R1_Tom.csv)

[\textcolor{purple}{Raw data - Hagai's table}](tables/Tom_VS_Hagai_R1_Hagai.csv)

### Table 7:

```{r, echo=FALSE}
library(tibble)
library(kableExtra)
DF1<- read.csv("tables/Tom_VS_Hagai_R1_Tom.csv") # My table
DF2<-read.csv("tables/Tom_VS_Hagai_R1_Hagai.csv") # Hagai's table
DF1$Dead.so.far<-with(DF1, 13-Live.Larvae) # made a new column calculate how many larvae died at that time
DF1[1,4]<- NA # Making first cell of dead so far empty
DF2$Dead.so.far<-with(DF2, 27-Live.Larvae)  # made a new column calculate how many larvae died at that time
DF2[1,4]<- NA # Making first cell of dead so far empty
# end of dataframe import
DF1[1,4]<- as.numeric(DF1[1,4])
DF2[1,4]<- as.numeric(DF2[1,4])
y<-c()
for (i in 1:length(DF1[,4])) {
  y<- append(y, (sum(as.numeric(DF1[2:i,4]))))
}
# y 
DF1$Accumulative.Dead <- y
s<- c()
for (i in 1:length(DF1[,4])) {
  s<- append(s, (as.numeric(DF1[i,5])/as.numeric(DF1[8,5]))*100)
}
# s
DF1$accu.dead.perc<-s

# Hagai
y<-c()
for (i in 1:length(DF2[,4])) {
  y<- append(y, (sum(as.numeric(DF2[2:i,4]))))
}
# y 
DF2$Accumulative.Dead <- y

s<- c()
for (i in 1:length(DF2[,4])) {
  s<- append(s, (as.numeric(DF2[i,5])/as.numeric(DF2[8,5]))*100)
}
# s
DF2$accu.dead.perc<-s

# End of making an accumulative column of dead %

# Naming headers and adding timeline for x axis ----
colnames(DF1)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
colnames(DF2)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
DF1$Time<- c(0,7,17,24,41,48,55,72)
DF2$Time<- c(0,7,17,24,41,48,55,72)

# Plotting ---- 

# plot(DF1[,7],DF1[,6], type = "b", main = "Tom's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# plot(DF2[,7],DF2[,6], type = "b", main = "Hagai's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# statistical

# summary(DF1)
# summary(DF2)
kable(DF1, booktabs = TRUE)
```

### Table 8:
```{r, echo=FALSE}
library(tibble)
library(kableExtra)
DF1<- read.csv("tables/Tom_VS_Hagai_R1_Tom.csv") # My table
DF2<-read.csv("tables/Tom_VS_Hagai_R1_Hagai.csv") # Hagai's table
DF1$Dead.so.far<-with(DF1, 13-Live.Larvae) # made a new column calculate how many larvae died at that time
DF1[1,4]<- NA # Making first cell of dead so far empty
DF2$Dead.so.far<-with(DF2, 27-Live.Larvae)  # made a new column calculate how many larvae died at that time
DF2[1,4]<- NA # Making first cell of dead so far empty
# end of dataframe import
DF1[1,4]<- as.numeric(DF1[1,4])
DF2[1,4]<- as.numeric(DF2[1,4])
y<-c()
for (i in 1:length(DF1[,4])) {
  y<- append(y, (sum(as.numeric(DF1[2:i,4]))))
}
# y 
DF1$Accumulative.Dead <- y
s<- c()
for (i in 1:length(DF1[,4])) {
  s<- append(s, (as.numeric(DF1[i,5])/as.numeric(DF1[8,5]))*100)
}
# s
DF1$accu.dead.perc<-s

# Hagai
y<-c()
for (i in 1:length(DF2[,4])) {
  y<- append(y, (sum(as.numeric(DF2[2:i,4]))))
}
# y 
DF2$Accumulative.Dead <- y

s<- c()
for (i in 1:length(DF2[,4])) {
  s<- append(s, (as.numeric(DF2[i,5])/as.numeric(DF2[8,5]))*100)
}
# s
DF2$accu.dead.perc<-s

# End of making an accumulative column of dead %

# Naming headers and adding timeline for x axis ----
colnames(DF1)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
colnames(DF2)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
DF1$Time<- c(0,7,17,24,41,48,55,72)
DF2$Time<- c(0,7,17,24,41,48,55,72)

# Plotting ---- 

# plot(DF1[,7],DF1[,6], type = "b", main = "Tom's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# plot(DF2[,7],DF2[,6], type = "b", main = "Hagai's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# statistical

# summary(DF1)
# summary(DF2)
kable(DF2, "latex", booktabs = TRUE)
```
### Graph 1:
```{r, echo=FALSE}
library(tibble)
library(kableExtra)
DF1<- read.csv("tables/Tom_VS_Hagai_R1_Tom.csv") # My table
DF2<-read.csv("tables/Tom_VS_Hagai_R1_Hagai.csv") # Hagai's table
DF1$Dead.so.far<-with(DF1, 13-Live.Larvae) # made a new column calculate how many larvae died at that time
DF1[1,4]<- NA # Making first cell of dead so far empty
DF2$Dead.so.far<-with(DF2, 27-Live.Larvae)  # made a new column calculate how many larvae died at that time
DF2[1,4]<- NA # Making first cell of dead so far empty
# end of dataframe import
DF1[1,4]<- as.numeric(DF1[1,4])
DF2[1,4]<- as.numeric(DF2[1,4])
y<-c()
for (i in 1:length(DF1[,4])) {
  y<- append(y, (sum(as.numeric(DF1[2:i,4]))))
}
# y 
DF1$Accumulative.Dead <- y
s<- c()
for (i in 1:length(DF1[,4])) {
  s<- append(s, (as.numeric(DF1[i,5])/as.numeric(DF1[8,5]))*100)
}
# s
DF1$accu.dead.perc<-s

# Hagai
y<-c()
for (i in 1:length(DF2[,4])) {
  y<- append(y, (sum(as.numeric(DF2[2:i,4]))))
}
# y 
DF2$Accumulative.Dead <- y

s<- c()
for (i in 1:length(DF2[,4])) {
  s<- append(s, (as.numeric(DF2[i,5])/as.numeric(DF2[8,5]))*100)
}
# s
DF2$accu.dead.perc<-s

# End of making an accumulative column of dead %

# Naming headers and adding timeline for x axis ----
colnames(DF1)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
colnames(DF2)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
DF1$Time<- c(0,7,17,24,41,48,55,72)
DF2$Time<- c(0,7,17,24,41,48,55,72)

# Plotting ---- 

plot(DF1[,7],DF1[,6], type = "b", main = "Tom's microinjection \naccumulative death count by percentage",
     xlab = "time passed since injection",
     ylab = "Percent of accumulated dead zf larvae" )

# plot(DF2[,7],DF2[,6], type = "b", main = "Hagai's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# statistical

# summary(DF1)
# summary(DF2)

```

### Graph 2:

```{r, echo=FALSE}
library(tibble)
library(kableExtra)
DF1<- read.csv("tables/Tom_VS_Hagai_R1_Tom.csv") # My table
DF2<-read.csv("tables/Tom_VS_Hagai_R1_Hagai.csv") # Hagai's table
DF1$Dead.so.far<-with(DF1, 13-Live.Larvae) # made a new column calculate how many larvae died at that time
DF1[1,4]<- NA # Making first cell of dead so far empty
DF2$Dead.so.far<-with(DF2, 27-Live.Larvae)  # made a new column calculate how many larvae died at that time
DF2[1,4]<- NA # Making first cell of dead so far empty
# end of dataframe import
DF1[1,4]<- as.numeric(DF1[1,4])
DF2[1,4]<- as.numeric(DF2[1,4])
y<-c()
for (i in 1:length(DF1[,4])) {
  y<- append(y, (sum(as.numeric(DF1[2:i,4]))))
}
# y 
DF1$Accumulative.Dead <- y
s<- c()
for (i in 1:length(DF1[,4])) {
  s<- append(s, (as.numeric(DF1[i,5])/as.numeric(DF1[8,5]))*100)
}
# s
DF1$accu.dead.perc<-s

# Hagai
y<-c()
for (i in 1:length(DF2[,4])) {
  y<- append(y, (sum(as.numeric(DF2[2:i,4]))))
}
# y 
DF2$Accumulative.Dead <- y

s<- c()
for (i in 1:length(DF2[,4])) {
  s<- append(s, (as.numeric(DF2[i,5])/as.numeric(DF2[8,5]))*100)
}
# s
DF2$accu.dead.perc<-s

# End of making an accumulative column of dead %

# Naming headers and adding timeline for x axis ----
colnames(DF1)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
colnames(DF2)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
DF1$Time<- c(0,7,17,24,41,48,55,72)
DF2$Time<- c(0,7,17,24,41,48,55,72)

# Plotting ---- 

# plot(DF1[,7],DF1[,6], type = "b", main = "Tom's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

plot(DF2[,7],DF2[,6], type = "b", main = "Hagai's microinjection \naccumulative death count by percentage",
     xlab = "time passed since injection",
     ylab = "Percent of accumulated dead zf larvae" )

# statistical

# summary(DF1)
# summary(DF2)

```

### Statistical analysis

#### DF1: 

```{r, echo=FALSE}
library(tibble)
library(kableExtra)
DF1<- read.csv("tables/Tom_VS_Hagai_R1_Tom.csv") # My table
DF2<-read.csv("tables/Tom_VS_Hagai_R1_Hagai.csv") # Hagai's table
DF1$Dead.so.far<-with(DF1, 13-Live.Larvae) # made a new column calculate how many larvae died at that time
DF1[1,4]<- NA # Making first cell of dead so far empty
DF2$Dead.so.far<-with(DF2, 27-Live.Larvae)  # made a new column calculate how many larvae died at that time
DF2[1,4]<- NA # Making first cell of dead so far empty
# end of dataframe import
DF1[1,4]<- as.numeric(DF1[1,4])
DF2[1,4]<- as.numeric(DF2[1,4])
y<-c()
for (i in 1:length(DF1[,4])) {
  y<- append(y, (sum(as.numeric(DF1[2:i,4]))))
}
# y 
DF1$Accumulative.Dead <- y
s<- c()
for (i in 1:length(DF1[,4])) {
  s<- append(s, (as.numeric(DF1[i,5])/as.numeric(DF1[8,5]))*100)
}
# s
DF1$accu.dead.perc<-s

# Hagai
y<-c()
for (i in 1:length(DF2[,4])) {
  y<- append(y, (sum(as.numeric(DF2[2:i,4]))))
}
# y 
DF2$Accumulative.Dead <- y

s<- c()
for (i in 1:length(DF2[,4])) {
  s<- append(s, (as.numeric(DF2[i,5])/as.numeric(DF2[8,5]))*100)
}
# s
DF2$accu.dead.perc<-s

# End of making an accumulative column of dead %

# Naming headers and adding timeline for x axis ----
colnames(DF1)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
colnames(DF2)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
DF1$Time<- c(0,7,17,24,41,48,55,72)
DF2$Time<- c(0,7,17,24,41,48,55,72)

# Plotting ---- 

# plot(DF1[,7],DF1[,6], type = "b", main = "Tom's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# plot(DF2[,7],DF2[,6], type = "b", main = "Hagai's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# statistical

summary(DF1)
# summary(DF2)

```


#### DF2:

```{r, echo=FALSE}
library(tibble)
library(kableExtra)
DF1<- read.csv("tables/Tom_VS_Hagai_R1_Tom.csv") # My table
DF2<-read.csv("tables/Tom_VS_Hagai_R1_Hagai.csv") # Hagai's table
DF1$Dead.so.far<-with(DF1, 13-Live.Larvae) # made a new column calculate how many larvae died at that time
DF1[1,4]<- NA # Making first cell of dead so far empty
DF2$Dead.so.far<-with(DF2, 27-Live.Larvae)  # made a new column calculate how many larvae died at that time
DF2[1,4]<- NA # Making first cell of dead so far empty
# end of dataframe import
DF1[1,4]<- as.numeric(DF1[1,4])
DF2[1,4]<- as.numeric(DF2[1,4])
y<-c()
for (i in 1:length(DF1[,4])) {
  y<- append(y, (sum(as.numeric(DF1[2:i,4]))))
}
# y 
DF1$Accumulative.Dead <- y
s<- c()
for (i in 1:length(DF1[,4])) {
  s<- append(s, (as.numeric(DF1[i,5])/as.numeric(DF1[8,5]))*100)
}
# s
DF1$accu.dead.perc<-s

# Hagai
y<-c()
for (i in 1:length(DF2[,4])) {
  y<- append(y, (sum(as.numeric(DF2[2:i,4]))))
}
# y 
DF2$Accumulative.Dead <- y

s<- c()
for (i in 1:length(DF2[,4])) {
  s<- append(s, (as.numeric(DF2[i,5])/as.numeric(DF2[8,5]))*100)
}
# s
DF2$accu.dead.perc<-s

# End of making an accumulative column of dead %

# Naming headers and adding timeline for x axis ----
colnames(DF1)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
colnames(DF2)<- c("Date checked", 
                  "Time of the day", 
                  "Live count", 
                  "Dead Count", 
                  "Dead accumulated", 
                  "Dead accumulated percentage")
DF1$Time<- c(0,7,17,24,41,48,55,72)
DF2$Time<- c(0,7,17,24,41,48,55,72)

# Plotting ---- 

# plot(DF1[,7],DF1[,6], type = "b", main = "Tom's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# plot(DF2[,7],DF2[,6], type = "b", main = "Hagai's microinjection \naccumulative death count by percentage",
#      xlab = "time passed since injection",
#      ylab = "Percent of accumulated dead zf larvae" )

# statistical

# summary(DF1)
summary(DF2)

```
