----------
9June2020
----------

# 19June2020 Fin clips, 19-20 May 2020 - Planning

Fin clip for mut zfGNE and model ZF from May 2020 
**Introduction:** During 19-20 may 2020 we collected fin flips from M743T KI ZF, mut zfGNE and hGNE zf KO models. 

**Strip Z contained KI ZF as follows**

| Strip position | Expected genotype | Fish physical position |
| :-------------:|-------------------|:----------------------:|
| 1              |  M743T            | A1                     |
| 2              |  M743T            | A2                     |
| 3              |  M743T            | A3                     |
| 4              |  Alon alpha actin |                        |
| 5              |  Alon alpha actin |                        |
| 6              |  M743T            | A6                     |
| 7              |  M743T            | A7                     |
| 8              |  M743T            | A8                     |

Even though we took FC of 4 and 5 (strip positions) we won't sequence them since there's no need to, we do need to breed them though. 

**strip y goes as follows:**

| strip position  | expected genotype          | fish physical position   |
| :-------------: | -------------------------- | :----------------------: |
| 1               | AB tg mut Cross TL zfGNE   | A9                       |
| 2               | AB tg mut Cross TL zfGNE   | A10                      |
| 3               | AB tg mut Cross TL zfGNE   | A11                      |
| 4               |                            |                          |
| 5               |                            |                          |
| 6               |                            |                          |
| 7               |                            |                          |
| 8               |                            |                          |

Beyond that we also got Strips A-D which contain FC from 15 dpf larvae that urgently need to be placed into a container.

\newpage
\blandscape

```{r, echo=FALSE}
x<-read.csv('tables/FCmaypoorlarvae.csv')
library(knitr)
library(kableExtra)
kable(x, "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```


\elandscape

\pagebreak{}{}

### PCR mixes:

**For Strip Z:**

```{r, echo=FALSE}
x<-read.csv('tables/9junePCRmix.csv')
library(knitr)
library(kableExtra)
kable(x, "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```

**For the rest:**

**WTS:**
```{r, echo=FALSE}
x<-read.csv('tables/9june2020PCRtableWTS.csv')
library(knitr)
library(kableExtra)
kable(x, "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```
**F1_2**
```{r, echo=FALSE}
x<-read.csv('tables/9june2020PCRF1_2.csv')
library(knitr)
library(kableExtra)
kable(x, "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = "striped")
```

\pagebreak{}{}

